---
title: "Project 2 Checkpoint"
author: "Alan Qin"
date: "2/27/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
  prettydoc::html_pretty:
    theme: architect
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("ggplot2")
data = read.csv("/Users/alanqin/Downloads/fifa-20-complete-player-dataset/players_20.csv")
data$release_clause_eur[is.na(data$release_clause_eur)]= 0
```


### Regression for different X's on wage

```{r lm 1}
fit_release = lm(data = data, wage_eur ~ release_clause_eur)
summary(fit_release)$adj.r.squared
```
The variables I chose were players' release clause and their value in euros. These values make sense because there 

```{r lm 2}
fit_value = lm(data = data, wage_eur ~ value_eur)
summary(fit_value)$adj.r.squared
```

```{r lm 3}
fit_pass = lm(data = data, wage_eur ~ passing)
summary(fit_pass)$adj.r.squared
```
The variables I chose were the players' passing and dribbling rating 
```{r lm 4}
fit_drib = lm(data = data, wage_eur ~ dribbling)
summary(fit_drib)$adj.r.squared
```
The variables I chose were the players' pace and defending rating
```{r lm 5}
fit_overall = lm(data = data, wage_eur ~ overall)
summary(fit_overall)$adj.r.squared
```
The variables I chose were the players' overall and potential rating 

```{r lm 6}
fit_potential = lm(data = data, wage_eur ~ potential)
summary(fit_potential)$adj.r.squared
```


The variables for this regression were release clause in euros, value in euros, weak foot,
skill moves, passing rating, dribbling rating, pace rating, defending rating, overall 
rating, and potential rating.


```{r lm best }
fit_best = lm(wage_eur ~ release_clause_eur + value_eur + overall +
                potential, data = data)
summary(fit_best)$adj.r.squared
```



### Y vs Yhat

```{r y vs yhat}
pred = fit_best$fitted.values
a = fit_release$fitted.values
b = fit_value$fitted.values
plot(pred,data$wage_eur)
plot(pred)
plot(data$wage_eur)
```

As you can see from the plot 

```{r}

```










